---
title: "How to fill the website"
author: "Sébastien Rochette"
date: "09/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Clone this project from github

- `git clone https://github.com/ThinkR-open/golemverse.org.git`

- Retrieve theme :
    + `git submodule update --init --recursive`

## Add content
### Add a post to "News" section

- Create a directory with name being the slug of the post under "content/post"
    + A slug has no space, no special character except `-`, everything in lowercase
- Create a ".Rmarkdown" file using {blogdown} addin "New Post" *or copy content from an existing one (which is easier)*. 
    + Save this file as **"index.Rmarkdown"** in the directory created above
- To add a featured image for the post, add an image called **"featured.png"** or **"featured.jpg"** in this same directory
    + Best dimension is 1024*512


### Add a new "Resources"

Add to the list in "content/home/resources".

### Add a new "Package"

- Create a directory with name being the slug of the post under "content/packages_list"
    + A slug has no space, no special character except `-`, everything in lowercase
- Create a ".Rmarkdown" file using {blogdown} addin "New Post" *or copy content from an existing one (which is easier)*. 
    + Save this file as **"index.Rmarkdown"** in the directory created above
- To add a featured image for the post, add an image called **"featured.png"** or **"featured.jpg"** in this same directory

## Add new stream

- Create a directory with name being the slug of the post under "content/talk"
    + A slug has no space, no special character except `-`, everything in lowercase
- Copy content from an existing one (which is easier). 
    + Save this file as **"index.Rmarkdown"** in the directory created above
- Fill `categories: ["stream"]`
- Fill other parameters in the YAML
- To add a featured image for the post, add an image called **"featured.png"** or **"featured.jpg"** in this same directory


Slides can be added in a few ways:

- **Create** slides using Academic's [*Slides*](https://sourcethemes.com/academic/docs/managing-content/#create-slides) feature and link using `slides` parameter in the front matter of the talk file
- **Upload** an existing slide deck to `static/` and link using `url_slides` parameter in the front matter of the talk file
- **Embed** your slides (e.g. Google Slides) or presentation video on this page using [shortcodes](https://sourcethemes.com/academic/docs/writing-markdown-latex/).

Further talk details can easily be added to this page using *Markdown* and $\rm \LaTeX$ math code.


## Structure of the website (active widgets)

The website is built on pages and widgets inside pages. 
The content of the website that can be modified in exclusively in the "content" directory. 
There are multiple directories, more or less linked to pages of the website.
Except for "post", each directory contain multiple ".md" files which are called widgets. 
They can be activated or not on the website.  

Below is the list of activated widgets and how to modify their content.  

See widgets available with the Academic theme: <https://sourcethemes.com/academic/docs/page-builder/>  

### Home

Content of home page is stored in "/content/home" directory.
This is a page with multiple widgets, activated or not.  

+ **hero.md**: Get started. 
    + <File to fill>
    + (weight = 10)
+ **skills.md**: Characteristics of the {golemverse} with icons.
    + <File to fill>
    + (weight = 30)
+ **featured.md**: One specific post to highlight whatever its time of publication.
    + <Only fill title and format. List of posts is read from "/post" directory with metadata: _featured_ set to `yes`>
    + (weight = 40)
+ **resources.md**: List of resources. 
    + <File to fill> with markdown syntax
    + (weight = 50)
+ **posts.md**: Recent News. 
    + <Only fill title and format. List of posts is read from "/post" directory>
    + (weight = 60)
+ **tags.md**: Tag cloud of post tags used.
    + <Only fill format. List of tags is issued in "tags" metadata of posts in "/post">
    + (weight = 120)
+ **contact.md**: Contacting ThinkR using formspree.io. 
    + <File to fill>
    + (weight = 130)

### Documentation

"Documentation" is a shortcut to "Documentation" section of the home page.
See **publications.md** in home page above.

### Packages




## Modify header menu

To modify header menu, go to "config/_default/menus.toml". 

## Modify footer

Modify HTML with Hugo template in "layouts/partials/site_footer.html"

## Modify favicon

Add an image with size 512*512 in `assets/images/icon.png`


## Update academic theme
Read news: https://sourcethemes.com/academic/updates

> Update hugo version required in `.travis.yml` if needed

If you installed by Git cloning hugo-academic

Before updating for the first time, the remote origin repository should be renamed to upstream:
```
cd themes/academic
git remote rename origin upstream
```
To list all available updates:
```
cd themes/academic
git fetch upstream
git log --pretty=oneline --abbrev-commit --decorate HEAD..upstream/master
```
Then, update by running:
```
git checkout <VERSION>
git pull upstream
```
where <VERSION> is defined in the previous section

## Update DESCRIPTION dependencies

```{r}
dirs <- list.dirs("content", recursive = FALSE)
# dir.exists(dirs)
res <- NULL
for (i in seq_along(dirs)) {
    res <- c(res, attachment::att_from_rmds(dirs[i], pattern = "*.(Rmd|rmd|Rmarkdown)$"))
}

pkg <- unique(c(res, "blogdown", "emo"))
attachment::att_to_desc_from_is(imports = pkg)
```

